---
output:
  md_document:
    variant: markdown_github
---

[![Travis-CI Build Status](https://travis-ci.org/dfalbel/ifelser.svg?branch=master)](https://travis-ci.org/dfalbel/ifelser)

[![Coverage Status](https://img.shields.io/coveralls/dfalbel/ifelser.svg)](https://coveralls.io/r/dfalbel/ifelser?branch=master)

## ifelser: package for more readable ifelse statements in R

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

If you ever had to make ifelse statements one inside of each other, this package will be usefull for you.

Think about the following code:

```{r}
x <- 1:10
ifelse(x<=5, 1, ifelse(x<=7.5, 2, ifelse(x<=9.2, 3, 4)))
```

It's hard to know what's being done. If x < 5 then x = 1 else if x <= 7.5 then
x = 2 else if 9.2 then x = 3 else x = 4.

The problem can be worse if variable names are longer and the statement does not fit one line.

```{r}
variable <- 1:10
ifelse(variable<=5, variable + log(variable), ifelse(variable<=7.5, variable + 2*log(variable), ifelse(variable<=9.2, variable + 3*log(variable), variable + 4*log(variable))))
```

Even if you think it's easy to understand the code, you won't find it easy to find if there are brackets missing.

Now take a look at `ifelser` code. It makes use of `magrittr` pipes to create more readable and mantainable code.

```{r}
library(ifelser)
test_if(variable <= 5) %>% 
  if_true(variable + log(variable)) %>% if_false() %>%
  test_if(variable <= 7.5) %>% 
  if_true(variable + 2*log(variable)) %>% if_false() %>%
  test_if(variable <= 9.2) %>% 
  if_true(variable + 3*log(variable)) %>% if_false(variable + 4*log(variable))
```

Don't think it's more readable?


